Coherent optical association of a single molecule

### 2020-11-09 paper.tex
Format and whitespace
Minor comments from Jeremy

\begin{abstract}
  Fully controlled single molecules provide a promising platform for a variety of quantum science applications. As a step towards this goal, we report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance.
  The Raman scheme uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing the photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69~\mathrm{\%}$.
  The molecule has a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$ 
  with more than $60~\mathrm{\%}$ of the molecule created in the motional ground state.
  This technique does not rely on narrow excited state lines or Feshbach resonances
  and will allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Kondov2019,Nick_and_Ivan2017, PhysRevA.101.042504, Andreev2018, PhysRevLett.119.153001, hudson2011}, quantum simulations~\cite{Micheli2006, Yao2018, Wall2015, wall2015realizing}, quantum information processing~\cite{DeMille2002, Ni2018, Hudson2018, Lin2019}, and studies of ultracold chemistry~\cite{Bala2016,Hu1111,Segev2019,deJongh626}.
While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016,Anderegg2018, Mitra1366, PhysRevX.10.021049, PhysRevLett.121.013202, Truppe2017}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020,He331}  have been achieved through the association of ultracold atoms.
% (any place to cite  molecular ion work?)
% Citations are not complete. Add them as you see fit.

Molecular association of ultracold atoms takes advantage of the cooling and trapping techniques that have been developed for atoms. Associating atoms into deeply-bound molecules is challenging because of the small wavefunction overlap between the free-atom and molecular state and the release of a large amount of binding energy. A two step approach has been demonstrated to associate atom pairs into weakly bound molecules first, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state releasing the binding energy via stimulated emission~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, most molecular association has been achieved for bialkali molecules by magnetoassociation using a magnetic Feshbach scattering resonance. The only exceptions are Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states are available and optical association can be driven coherently,~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb, where weakly-bound molecules with a couple MHz binding energy exists~\cite{He331}. With these requirements, molecules involving non-magnetic atoms or atoms without narrow intercombination lines remain difficult to associate.
% These requirements limit the generality of previous association techniques.
% The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques. % to more diverse species.

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}a. The scheme does not rely on a Feshbach resonance, few MHz level bound states, or a narrow excited state. The resulting single molecule is in a well-defined internal quantum state and predominately in its motional ground state. A vibrational state of the electronic excited state $\mathrm{c^3\Sigma^+}(\Omega = 1)$ is used as the intermediate state in the Raman scheme, and is chosen to minimize the theoretical photon scattering during a Raman Rabi oscillation. To further reduce the photon scattering and sensitivity to laser intensity noise, we choose the initial and final state to balance the two Rabi frequencies as much as possible. This system-independent approach can be used for creating new molecules atom-by-atom with full quantum state control.

\begin{figure*}
  \includegraphics[width=\textwidth]{fig1.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (a) Schematic of the optical transition from an atom pair to a weakly-bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $\mathrm{c^3\Sigma}$ potential
    by $\Delta$ in order to suppress the scattering during the transfer.
    (b) Comparison between using a weakly-bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (upper half $v'=0$)
    has a smaller Raman Rabi frequency ($\Omega_{R}$)
    compared to the weakly-bound excited state (lower half $v'=63$) at a given detuning.
    However, the scattering rate ($\Gamma_{s}$) is also much lower,
    which results in a larger Raman Rabi frequency to scattering rate ratio.
    (c) Enhancement of the short range wavefunction.
    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction especially at short
    intranuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\text{\AA}$, left of the dotted line)
    is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}a), where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
The transfer Raman Rabi Rate, $\Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate $\Gamma_e (\Omega_a^2 + \Omega_m^2)/4\Delta^2$
% $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
~\cite{Wineland2003}.
Unlike Raman transitions in atoms, the two Rabi frequencies are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
and therefore the scattering is predominantly from the target molecular state. Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally. Thus, the scattering rate is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power. Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
The ratio between the Raman Rabi frequency and the scattering rate is therefore $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $. %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.

Early experiments used weakly bound excited states as the intermediate state
in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
However, for a complete picture, the many excited vibrational states in a molecular potential
as well as the excited atomic continuum need to be considered.
The total scattering rate and Raman Rabi rate become a sum of the scattering rates
and Raman Rabi rates over all possible intermediate states.
With these considerations, using a weakly bound excited state as the intermediate state
suffers from strong scattering of the nearby excited atomic continuum, resulting in large incoherence and loss to other molecular states.
This scattering is proportional to $1/\delta_{\mathrm{thresh}}^2$,
where $\delta_{\mathrm{thresh}}$ is the detuning from the dissociation threshold,
and thus can be made smaller by using deeply bound vibrational states as the intermediate level.

To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency $\Omega_R$
and scattering rate $\Gamma_s$ at different detunings from the atomic threshold
taking into account of all states of
the $\mathrm{c^3\Sigma^+}(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011}
and the continuum~\cite{Liu2017}.
The excited atomic continuum is particularly important for the target molecular state.
The sum of the squares of the wavefunction overlap
between the target weakly-bound molecular state
and all the excited molecular bound states is only about $0.02$,
suggesting that there is significant matrix element
between the target molecular state and the excited atomic continuum (See Supplementary Material\todo{proper cite}).
This calculation shows that the ratio of the Raman Rabi rate to scattering rate
can be made larger for more deeply bound states compared to weakly bound states
at a cost of a smaller Raman Rabi frequency
(Fig.~\ref{f-theory}b, full result in Supplementary Material \todo{proper cite})
As a result, we choose the $v'=0$ of $\mathrm{c^3\Sigma^+}(\Omega = 1)$ as an intermediate state
to drive the Raman transition.

@@

choosing an initial and a final state for a large $ \Omega_a/\Omega_m $ ratio

@@

Due to the small size of the intermediate state wavefunction as compared to the trapped atoms,

@@

the value of the relative atomic wavefunction at short distance
within the molecular potential.
To increase the amplitude within the molecular potential,
one can increase the external confinement of atom pairs.
Using a harmonic oscillator approximation,
the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $ or $P^{3/8}$,

@@

For these states, the phase shift in the relative wavefunction
between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}c).

@@

we choose a spin state combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=3,m_F=3}_{\Cs}$ that has a large and negative scattering length of
$ a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0$~\cite{Hood2019}.

@@

Coupled channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $,
with the intermediate state when compared to bound states of the other spin compositions. This further increases the $\Omega_a/\Omega_m$ ratio when using the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.

@@

results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003

@@

% \textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure}[ht!]
  \includegraphics[width=0.48\textwidth]{fig2.pdf}
  \caption{
    (a) Raman detuning scans at different times showing the resonance frequency.
    (b) Raman pulse time scan on resonance.
    A decaying Rabi oscillation can be observed proving the coherence of
    the Raman transfer process.
    This is fitted together with (a) to a model of the Raman transition including loss of the atom and molecule state and is used to determine
    both the Raman Rabi frequency and the loss rates.
    Inset: Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to a waist of $0.9~\mathrm{\mu m}$
    which defines the location of the atoms and molecule.
    We use a bias B field of $B_0=8.8~\mathrm{G}$ along the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experiences predominately $\pi$ polarization from the tweezer.
    \label{f-raman}}
\end{figure}

%% Preparation
Experimentally, we first prepare two atoms in a well-defined external and internal quantum state using techniques developed previously~\cite{Liu2018, Liu2019, Wang2019}. In brief, the experimental cycle begins by stochastically loading a single ${}^{23}\Na$ atom and a single ${}^{133}\Cs$ atom into separate optical tweezers. The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom to be able to post select the experimental result on the initial loading condition. Raman sideband cooling is then applied to prepare both atoms simultaneously into the 3-dimensional motional ground state of their optical tweezers. After cooling, the Na and Cs atoms are in a spin state of $\ket{\uparrow_{\Na}\uparrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=4,m_F=4}_{\Cs} $ %and are merged into the same tweezer~\cite{Liu2019}. %The spin states for the Na and Cs atoms after RSC and during the merge process are $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $.
which has a small scattering length. The small two atom interaction allows the merging of the two atoms to be done with minimum pertubation so that they remain in the motional ground state.

% After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
Next, we drive the atoms into the large scattering length $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination to use as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7~\mathrm{kHz}$ interaction shift~\cite{Hood2019}.  %using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\Cs}}$ state. The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer.
This spin flip selectively transfers atoms in the relative motional ground state, removing any initial hot atom background from imperfect cooling \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motional ground state.}. For the experiment reported here, $31~\mathrm{\%}$ of our initial two atom population is successfully transferred.
% of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..

%% Transfer scheme
% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
To perform the Raman transfer of an atom pair to the target weakly bound molecular state, we use the tweezer beam itself as the Raman beams by turning on two frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}b inset). The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to maximize the Raman Rabi frequency and minimize the transfer time. Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50 ~\mathrm{GHz}$ to filter the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser. We observed a reduction of the scattering rate by a factor of $2$ due to suppression of the broadband amplified spontaneous emission (ASE) from the laser that couples to other excited states. % to allow perfect overlap and to eliminate additional beams and therefore scattering sources.
After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a specified duration before the process is reversed and the tweezer returns to a single frequency.
% In addition to reducing the number of laser beams during the Raman transition,

% found the spectral purity of the laser for Raman beams to be critical for achieving a higher transfer efficiency.
% The tweezer/Raman beams are generated by a fiber amplifier seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
% by amplifying a $1037~\mathrm{nm}$ external cavity diode laser (ECDL) with a fiber amplifier,
% The diode laser produces the desired frequency on top of a broad band amplified spontaneous emission (ASE).  We use a Bragg grating with a line width (FWHM) of $50~\mathrm{GHz}$ to clean up the laser spectrum and found it reduces the scattering rate by at least a factor of $2$
% for a particular single photon detuning.

>>>>

\begin{abstract}
  Fully controlled single molecules provide a promising platform
  for a variety of quantum science applications.
  As a step towards this goal, we report on coherent association
  of a single weakly bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance.
  The Raman scheme uses a deeply bound electronic excited intermediate state
  to achieve a large transition dipole moment while reducing the photon scattering.
  Starting from two atoms in their relative motional ground state,
  we achieve an optical transfer efficiency of $69~\mathrm{\%}$.
  The molecule has a binding energy of $770.20052(2)~\mathrm{MHz}$ at $8.8~\mathrm{G}$
  with more than $60~\mathrm{\%}$ of the molecule created in the motional ground state.
  This technique does not rely on narrow excited-state lines or Feshbach resonances
  and will allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

Diverse species of fully quantum controlled  ultracold molecules are desired
for a wide variety of applications including precision measurements~\cite{
  Kondov2019,Nick_and_Ivan2017, PhysRevA.101.042504, Andreev2018,
  PhysRevLett.119.153001, hudson2011},
quantum simulations~\cite{Micheli2006, Yao2018, Wall2015, wall2015realizing},
quantum information processing~\cite{DeMille2002, Ni2018, Hudson2018, Lin2019},
and studies of ultracold chemistry~\cite{Bala2016,Hu1111,Segev2019,deJongh626}.
While many innovative approaches demonstrated in the last few years
have directly cooled different species of diatomic or polyatomic molecules
below 1~mK~\cite{Norrgard2016,Anderegg2018, Mitra1366, PhysRevX.10.021049,
  PhysRevLett.121.013202, Truppe2017},
the highest phase-space-density gas~\cite{Demarco2018} and
the coldest individual molecules~\cite{Zhang2020,He331}
have been achieved through the association of ultracold atoms.
% (any place to cite molecular ion work?)
% Citations are not complete. Add them as you see fit.

Molecular association of ultracold atoms takes advantage of the cooling and trapping techniques
that have been developed for atoms.
Associating atoms into deeply-bound molecules is challenging
because of the small wavefunction overlap between the free-atom and molecular states
and the release of a large amount of binding energy.
A two-step approach has been demonstrated to associate atom pairs
into weakly bound molecules first,
and then transfer the molecules from this single internal state
to a desired rovibrational and electronic state,
releasing the binding energy by stimulated emission~\cite{Danzl2008, Ni2008, Lang2008,
  Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, most molecular association has been achieved for bialkali molecules
by magnetoassociation using a magnetic Feshbach scattering resonance.
The only exceptions are Sr$_2$, where narrow linewidth ($\sim 20~\mathrm{kHz}$) excited states
are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012},
and $^{87}$Rb$^{85}$Rb,
where there are molecular states bound by $1\sim2~\mathrm{MHz}$~\cite{He331}.
With these requirements, molecules involving non-magnetic atoms
or atoms without narrow intercombination lines remain difficult to associate.
% These requirements limit the generality of previous association techniques.
% The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited-state lines limits the generality of previous association techniques. % to more diverse species.

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule
using a two-photon optical Raman transfer via an electronic excited state,
schematically shown in Fig.~\ref{f-theory}a.
The scheme does not rely on a Feshbach resonance,
molecular states bound by a few MHz, or a narrow excited state.
The resulting single molecule is in a well-defined internal quantum state
and predominantly in its motional ground state.
A vibrational state of the electronic excited state $\mathrm{c^3\Sigma^+}(\Omega = 1)$
is used as the intermediate state in the Raman scheme,
and is chosen to minimize the theoretical photon scattering during a Raman Rabi oscillation.
To reduce the photon scattering and sensitivity to laser intensity noise further,
we choose the initial and final state to balance the two Rabi frequencies as much as possible.
This system-independent approach can be used for creating new molecules atom-by-atom
with full quantum state control.

\begin{figure*}
  \includegraphics[width=\textwidth]{fig1.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (a) Schematic of the optical transition from an atom pair to a weakly bound molecule.
    The initial state is the relative motional ground state between the two atoms
    and the final state is the first molecular bound state.
    The transition is driven by a pair of laser frequencies matching the binding energy
    of the molecule.
    The lasers are detuned from an excited molecular state in the $\mathrm{c^3\Sigma}$ potential
    by $\Delta$ in order to suppress the scattering during the transfer.
    (b) Comparison between using a weakly bound and a deeply bound excited state
    as intermediate state for the Raman transition.
    The deeply bound excited state (upper half $v'=0$)
    has a smaller Raman Rabi frequency ($\Omega_{R}$)
    compared to the weakly bound excited state (lower half $v'=63$) at a given detuning.
    However, the scattering rate ($\Gamma_{s}$) is also much lower,
    which results in a larger Raman Rabi frequency to scattering rate ratio.
    (c) Enhancement of the short-range wavefunction.
    The large scattering length for the $\Na(2,2),\Cs(3,3)$ state creates an interaction shift
    comparable to the axial trapping frequency.
    This causes a significant change in the relative wavefunction especially at short
    intranuclear distance ($R$).
    Compared to other spin states with weaker interaction,
    the wavefunction at short distance ($R<100\text{\AA}$, left of the dotted line)
    is significantly enhanced.
    \label{f-theory}
  }
\end{figure*}

The essence of an optical Raman transfer can be illustrated
using a three-level system shown in Fig.~\ref{f-theory}a,
where the initial atomic state and the target weakly bound molecular state are coupled to an intermediate state by two lasers with Rabi frequencies, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $\mathrm{c^3\Sigma^+}$)
The transfer Raman Rabi Rate, $\Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate $\Gamma_e (\Omega_a^2 + \Omega_m^2)/4\Delta^2$
% $\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
~\cite{Wineland2003}.
Unlike Raman transitions in atoms, the two Rabi frequencies are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
and therefore the scattering is predominantly from the target molecular state. Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single-photon detuning, $ \Delta $, so the target molecular state can scatter off both beams roughly equally. Thus, the scattering rate is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited-state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi rate at a fixed total power. Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
The ratio between the Raman Rabi frequency and the scattering rate is therefore $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $. %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth.
To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.

Early experiments used weakly bound excited states as the intermediate state
in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
However, a complete picture must include both the many vibrational levels
of the excited electronic state and the atomic continuum.
The total scattering rate and Raman Rabi rate become a sum of the scattering rates
and Raman Rabi rates over all possible intermediate states.
With these considerations, using a weakly bound excited state as the intermediate state
suffers from strong scattering due to the nearby excited atomic continuum,
resulting in large incoherence and loss to other molecular states.
This scattering is proportional to $1/\delta_{\mathrm{thresh}}^2$,
where $\delta_{\mathrm{thresh}}$ is the detuning from the dissociation threshold,
and thus can be made smaller by using deeply bound vibrational states as the intermediate level.

To find the optimal intermediate state, we perform a calculation of the Raman Rabi frequency $\Omega_R$
and scattering rate $\Gamma_s$ at different detunings from the atomic threshold
taking into account of all states of
the $\mathrm{c^3\Sigma^+}(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011}
and the continuum~\cite{Liu2017}.
The excited atomic continuum is particularly important for the target molecular state.
The sum of the squares of the wavefunction overlap
between the target weakly bound molecular state
and all the excited molecular bound states is only about $0.02$,
suggesting that there are significant matrix elements
between the target molecular state and the excited atomic continuum.
This calculation shows that the ratio of the Raman Rabi rate to scattering rate
can be made larger for more deeply bound states compared to weakly bound states
at a cost of a smaller Raman Rabi frequency, as shown in Fig.~\ref{f-theory}b;
see Supplementary Material for details.
As a result, we choose the $v'=0$ level of $\mathrm{c^3\Sigma^+}(\Omega = 1)$
as an intermediate state to drive the Raman transition.

@@

choosing an initial and a final state for a large ratio $\Omega_a/\Omega_m$

@@

Due to the small extent of the intermediate-state wavefunction
compared to that of the trapped atoms,

@@

the amplitude of the relative atomic wavefunction at short distance,
within the range of the molecular potential.
To increase this amplitude, one can increase the external confinement of atom pairs.
Using a harmonic approximation,
the short-range amplitude is proportional to $ \omega_{\text{trap}}^{3/4} $ or $P^{3/8}$,

@@

For such states, the amplitude of the relative atomic wavefunction is substantially enhanced
at short range, as shown in Fig.~\ref{f-theory}c.

@@

we choose a spin-state combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=3,m_F=3}_{\Cs}$ that has a large and negative scattering length of
$a(\uparrow_{\Na} \downarrow_{\Cs}) = -693.8a_0$~\cite{Hood2019}.

@@

coupled-channel calculations show that this target molecular state with similar spin composition also has reduced Rabi frequency, $ \Omega_m $,
with the intermediate state when compared to bound states of the other spin compositions. This further increases the ratio $\Omega_a/\Omega_m$ when using the $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$ hyperfine combination.

@@

results in a ratio $\Omega_a/\Omega_m$ of about 0.05 instead of a ratio of about 0.003

@@

% \textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled-channel calculation anywhere...)

% In additional to the final and the excited state, it is also important to select the an initial atomic state in order to improve the coupling.
\begin{figure}[ht!]
  \includegraphics[width=0.48\textwidth]{fig2.pdf}
  \caption{
    (a) Raman detuning scans at different times showing the resonance frequency.
    (b) Raman pulse time scan on resonance.
    A decaying Rabi oscillation can be observed proving the coherence of
    the Raman transfer process.
    This is fitted together with (a) to a model of the Raman transition including loss of the atom and molecule state and is used to determine
    both the Raman Rabi frequency and the loss rates.
    Inset: Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    The tweezer and Raman beam is focused through an objective to a waist of $0.9~\mathrm{\mu m}$
    which defines the location of the atoms and molecule.
    We use a bias B field of $B_0=8.8~\mathrm{G}$ along the tweezer polarization
    to define the quantization axis.
    As a result, the atoms experiences predominantly $\pi$ polarization from the tweezer.
    \label{f-raman}}
\end{figure}

%% Preparation
Experimentally, we first prepare two atoms in a well-defined external and internal quantum state
using techniques developed previously~\cite{Liu2018, Liu2019, Wang2019}.
In brief, the experimental cycle begins by stochastically loading a single ${}^{23}\Na$ atom
and a single ${}^{133}\Cs$ atom into separate optical tweezers.
The atoms are initially imaged to distinguish between loading of two atoms,
one atom (Na or Cs), or no atom to be able to post-select from the experimental results
based on the initial loading condition.
Raman sideband cooling is then applied to prepare both atoms simultaneously
in the 3-dimensional motional ground state of their optical tweezers.
After cooling, the Na and Cs atoms are in the spin state~$\ket{\uparrow_{\Na}\uparrow_{\Cs}}\equiv \ket{F=2,m_F=2}_{\Na}\ket{F=4,m_F=4}_{\Cs}$,
which has a small scattering length.
The weak two-atom interaction allows the merging of the two tweezers to be done
with minimum pertubation so that they remain in the motional ground state.

% After preparing the Na and Cs atoms in the same tweezer in a single quantum state,
Next, we drive the atoms into spin combination $\ket{\uparrow_{\Na} \downarrow_{\Cs}}$,
which has large scattering length,
by performing a Cs spin flip while taking into account
the $-30.7~\mathrm{kHz}$ interaction shift~\cite{Hood2019}.
We use this as the initial atomic state for Raman transfer.
This spin flip selectively transfers atoms in the relative motional ground state,
removing any background from atoms in excited motional states
\footnote{This interaction shift is larger than the differential axial trapping frequency
  between Na and Cs atoms, which decouples the relative and center of mass motional state
  and improves the robustness of our preparation of the relative motional ground state.}.
For the experiment reported here,
$31~\mathrm{\%}$ of our initial two-atom population is transferred.
% of two atoms loaded in separate optical tweezers.\textcolor{red}{I also find this part of the sentence confusing.  can you say this more concisely?}\todo{}
% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..

%% Transfer scheme
% After the atoms are prepared in the $\ket{\uparrow_{\Na}\uparrow_{\Cs}} $ hyperfine combination, we then perform the Raman transfer.
To perform the Raman transfer of an atom pair to the target weakly bound molecular state,
we use the tweezer beam itself as the Raman beams by turning on two frequencies
in the tweezer during the Raman pulse, as shown in Fig.~\ref{f-raman}b inset.
The dual use of the tweezer beam not only eliminates additional scattering sources
or undesired laser frequencies,
but also allows a tight focus to maximize the Raman Rabi frequency
and minimize the transfer time.
Furthermore, we use a Bragg grating with a linewidth (FWHM) of $50~\mathrm{GHz}$
to filter the laser spectrum generated by a fiber amplifier
that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
We observe a reduction of the scattering rate by a factor of $2$
due to suppression of the broadband amplified spontaneous emission (ASE) from the laser
that couples to other excited states.
After the total tweezer power is set to the desired value,
we smoothly ramp down the power of one frequency in the tweezer
while simultaneously ramping up the power of a different frequency
so that the total tweezer power remains unchanged.
Both frequencies are kept on for a specified duration before the process is reversed
and the tweezer returns to a single frequency.

% found the spectral purity of the laser for Raman beams to be critical for achieving a higher transfer efficiency.
% The tweezer/Raman beams are generated by a fiber amplifier seeded with a $1037~\mathrm{nm}$ external cavity diode laser.
% by amplifying a $1037~\mathrm{nm}$ external cavity diode laser (ECDL) with a fiber amplifier,
% The diode laser produces the desired frequency on top of a broad band amplified spontaneous emission (ASE).  We use a Bragg grating with a line width (FWHM) of $50~\mathrm{GHz}$ to clean up the laser spectrum and found it reduces the scattering rate by at least a factor of $2$
% for a particular single-photon detuning.
